Consensus Problems in Networks of Agents\\ with Switching Topology and Time-Delays

### 2020-10-28 Paper.tex
Update Caption of Figures

{\color[gray]{0.5}
The key in the stability analysis of system (6) is in the spectral properties of graph Laplacian. 
The following result is well-known (e.g. see [17]) and is based on Gerˇsgorin disk theorem [12].
}

系统(\ref{6})稳定性分析的关键是拉普拉斯图的谱图特性。
接下来的结果已经众所周知（例如，文献[17]），它是基于Gesgorin圆盘定理（Gersgorin disk theorem），参考文献[12]。

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=8cm]{figures/Fig1-DiskTheorem.jpeg}
    \caption{圆盘定理应用在图拉普拉斯的效果演示}
    \label{DiskTheorem}
\end{figure}

{\color[gray]{0.5}
\noindent \textbf{Proof.}  Based on the Gerˇsgorin disk theorem, all the eigenvalues of $L=[l_{ij}]$ are located in the union of the following $n$ disks
}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4cm]{figures/Fig2-ConnectedDigraph.jpeg}
    \label{ConnectedDigraph}
    \caption{一个不能使用协议(\ref{A1})解决平均一致性问题的3阶连通图}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=12cm]{figures/Fig3-BalancedGraphs.jpeg}
    \label{BalancedGraphs}
    \caption{平衡图的三个例子}
\end{figure}

@@

{\color[gray]{0.5}
Based on part i) of Theorem 10, one concludes that the upper bound on the admissible channel time-delay in the network is inversely proportional to $\lambda_n$， i.e. the largest eigenvalue of the Laplacian of the information flow. 
From Gersgorin theorem, we know that $\lambda_n\le 2d_{max}(G)$, where $d_{max}(G)$ is the maximum out-degree of the nodes of $G$. 
Therefore, a sufficient condition for convergence of protocol (A2) is 
}

@@

% ------------------------------------------------------------------------------
\section{Simulation Results}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=12cm]{figures/Fig4-BalancedSC.jpeg}
    \label{Fig4}
    \caption{强连接的平衡图}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=14.5cm]{figures/Fig5-Simulation.jpeg}
    \label{Simulation}
    \caption{图的轨迹}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=14.5cm]{figures/Fig6-Automaton.jpeg}
    \label{Automaton}
    \caption{有限自动机}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=8cm]{figures/Fig7-Undirected.jpeg}
    \label{Undirected}
    \caption{用作沟通时滞一致性的无向图$G_e$}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=14.5cm]{figures/Fig8-ConsensusProblem.jpeg}
    \label{ConsensusProblem}
    \caption{一致性问题}
\end{figure}

>>>>

{\color[gray]{0.5}
The key in the stability analysis of system (6) is in the spectral properties of graph Laplacian. 
The following result is well-known (e.g. see [17]) and is based on Ger\v sgorin disk theorem [12].
}

系统(\ref{6})稳定性分析的关键是拉普拉斯图的谱图特性。
接下来的结果已经众所周知（例如，文献[17]），它是基于Gesgorin圆盘定理（Ger\v sgorin disk theorem），参考文献[12]。

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=8cm]{figures/Fig1-DiskTheorem.jpeg}
    \caption{A demonstration of Ger\v sgorin Theorem applied to graph Laplacian.}
    \label{DiskTheorem}
\end{figure}

{\color[gray]{0.5}
\noindent \textbf{Proof.}  Based on the Ger\v sgorin disk theorem, all the eigenvalues of $L=[l_{ij}]$ are located in the union of the following $n$ disks
}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4cm]{figures/Fig2-ConnectedDigraph.jpeg}
    \label{ConnectedDigraph}
    \caption{A connected digraph of order 3 that does not solve the average-consensus problem using Protocols (A1)}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=12cm]{figures/Fig3-BalancedGraphs.jpeg}
    \label{BalancedGraphs}
    \caption{Three examples of balanced graphs.}
\end{figure}

@@

{\color[gray]{0.5}
Based on part i) of Theorem 10, one concludes that the upper bound on the admissible channel time-delay in the network is inversely proportional to $\lambda_n$， i.e. the largest eigenvalue of the Laplacian of the information flow. 
From Ger\v sgorin theorem, we know that $\lambda_n\le 2d_{max}(G)$, where $d_{max}(G)$ is the maximum out-degree of the nodes of $G$. 
Therefore, a sufficient condition for convergence of protocol (A2) is 
}

@@

% ------------------------------------------------------------------------------
\section{Simulation Results}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=12cm]{figures/Fig4-BalancedSC.jpeg}
    \label{Fig4}
    \caption{For examples of balanced and strongly connected digraphs: (a) $G_a$, (b) $G_b$, (c) $G_c$, and (d) $G_d$ satisfying.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=14.5cm]{figures/Fig5-Simulation.jpeg}
    \label{Simulation}
    \caption{For examples of balanced and strongly connected digraphs: (a) $G_a$, (b) $G_b$, (c) $G_c$, and (d) $G_d$ satisfying.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=14.5cm]{figures/Fig6-Automaton.jpeg}
    \label{Automaton}
    \caption{(a) A finite automaton with for states representing the discrete-states of a network with variable topology and (b) trajectory of the node values and the group disagreement for a network with a switching information flow.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=8cm]{figures/Fig7-Undirected.jpeg}
    \label{Undirected}
    \caption{Undirected graph $G_e$ used for consensus with communication time-delays}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=14.5cm]{figures/Fig8-ConsensusProblem.jpeg}
    \label{ConsensusProblem}
    \caption{Consensus problem with communication time-delay on $G_b$ in Figure 7: (a)$\tau$=0, (b)$\tau=0.5\tau_{max}$, (c)$\tau=0.7\tau_{max}$, and (d)$\tau=\tau_{max}$ .}
\end{figure}
